Verifying Demonstrations

### 2018-10-31 paper/privacy-properties.tex
temporariliy restored privacy property text previously removed

\daniel{I suggest ending here to continue in \cref{adversary-model}. I've now 
  added P1 and P2.}

\sonja{discussion about applicable properties here, more sources and 
  alternative properties}
\sonja{new}
Difference to e-voting:
physical presence means support for a cause if there is one protest. If there is a counterprotest, physical presence with that group means support for the counterprotest. In our system, it gets more ambiguous as the participants are counted if all of the following is true
\begin{enumerate*}
\item they participate in the protocol,
\item they use the protest identifier (cause) for which the count is done,
\item they meet the eligibility criteria, and
\item they receive enough proof shares,
\item that are uploaded to the ledger.
\end{enumerate*}
Thus one could participate in a protest and be counted even when physically 
present at a counter-protest if the two protests are co-located and the 
participant chooses the corresponding cause/identifier of the original protest.

@@

As a consequence, this leaves us with with what would correspond to vote privacy.
In particular, we need unlinkability between Alice's long-term identity and Alice's participation proof.
Given a participation proof, Grace will not be able to tell if it belongs to Alice or Bob.
Furthermore, if Grace has managed to link one proof to Alice's, she should not be able to link another proof (\eg, from a different protest) as a consequence.
Hence, we can summarize the needed privacy properties as follows:
\begin{requirements}[P]
\item\label{ProofUnlink} \emph{Anonymity}: participants must be unlinkable to their proofs.
\item\label{ProtestUnlink} \emph{Unlinkability}: participants (or proofs issued by the same participant) must be unlinkable between different protests.
\end{requirements}

>>>>

\sonja{new}
Difference to e-voting:
physical presence means support for a cause if there is one protest. If there is a counterprotest, physical presence with that group means support for the counterprotest. In our system, it gets more ambiguous as the participants are counted if all of the following is true
\begin{enumerate*}
\item they participate in the protocol,
\item they use the protest identifier (cause) for which the count is done,
\item they meet the eligibility criteria, and
\item they receive enough proof shares,
\item that are uploaded to the ledger.
\end{enumerate*}
Thus one could participate in a protest and be counted even when physically 
present at a counter-protest if the two protests are co-located and the 
participant chooses the corresponding cause/identifier of the original protest.

@@

As a consequence, this leaves us with with what would correspond to vote privacy.
In particular, we need unlinkability between Alice's long-term identity and Alice's participation proof.
